untitled

### 2016-04-23 model.tex
typo

\begin{align}
  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0,\\
  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, 
\end{align}
with $s = \ln{P/\rho^\gamma}$. These criteria are applicable to any adiabatic fluid. 
For the present dusty problem, we may take 
where $\kappa^2 \equiv r^{-3}\p_r\left(r^4\Omega^2\right)$ is the
square of the epicylic frequency. We assume $\kappa^2>0$. 
These criteria are applicable to any adiabatic fluid when $s$
is the usual definition of entropy. For the dusty problem, we may take 
$s=\ln{(1-\epsilon)}+\mathrm{const.}$ from the definition of $s$ and  
the equation of state (Eq. \ref{eos}) with uniform sound-speed.

>>>>

\begin{align}
  \kappa^2 - \frac{1}{\rho}\nabla P \cdot \nabla s &> 0,\\
  -\frac{1}{\rho}\frac{\p P}{\p z} \left(\kappa^2 \frac{\p s}{\p z} -
  r\frac{\p\Omega^2}{\p z}\frac{\p s}{\p r}\right) &>0, 
\end{align}
with $s = \ln{P/\rho^\gamma}$ and 
$\kappa^2 \equiv r^{-3}\p_r\left(r^4\Omega^2\right)$ is the
square of the epicylic frequency. We assume $\kappa^2>0$. 
These criteria are applicable to any adiabatic fluid when $s$
is the usual definition of entropy. For the dusty problem, we may take 
$s=\ln{(1-\epsilon)}+\mathrm{const.}$ from the definition of $s$ and  
the equation of state (Eq. \ref{eos}) with uniform sound-speed.
